---
title: "Lab 3"
author: "Katie Denning & Tamara Niella"
date: "April 22, 2020"
output: 
  html_document:
    toc: true
    toc_float: true
    dev: png
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidymodels)
```

## Read in the `train.csv` data. Please feel free to use `sample_frac()` if you find that the data file is too large for your machine.

```{r, data}
# Reading in the data
df <- read_csv(here::here("data", "train.csv")) %>% 
  as_tibble()

```


## 1. Initial Split

Set a seed and split the data into a training set and a testing set as two named objects. 

```{r, initial_split}
set.seed(210)
split <- initial_split(df)

train_set <- training(split)
test_set <- testing(split)

```

## 2. Resample

Set a seed and use 10-fold cross-validation to resample the traning data.

```{r, resample}
set.seed(210)
cv_splits <- vfold_cv(train_set)
#cv_splits
```

## 3. Preprocess

Complete the code maze below by filling in the blanks (____) to create a recipe object that includes:
* a formula model with `score` predicted by 4 predictors
* be sure there are no missing data in your predictors (try `step_naomit()`)
* center and scale all numeric predictors
* dummy code all nominal predictors

```{r, preprocess}

lasso4_rec <- 
  recipe(
    formula = score ~ ethnic_cd + econ_dsvntg + gndr + migrant_ed_fg, 
    data = train_set #use your training set here
  ) %>%
  step_naomit(everything(), skip = TRUE) %>% 
  step_string2factor(econ_dsvntg, gndr, ethnic_cd, migrant_ed_fg) %>%  #may not need, depending on your formula
  step_dummy(econ_dsvntg, gndr, ethnic_cd, migrant_ed_fg) #%>% #may not need, depending on your formula
  #step_normalize() #may not need, depending on your formula

```

## 4. Parsnip model

Create a `{parsnip}` lasso model where the penalty hyperparameter is set to be tuned.

```{r, lasso}
mod_lasso <- linear_reg() %>%
  set_engine("glmnet") %>% 
  set_mode("regression") %>% # redundant; just getting in the habit
  set_args(penalty = tune(), # we set the penalty = .1 
           mixture = 1) # specifies a lasso regression model
```

## 5. Fit a tuned lasso model

Complete the code maze below to fit a tuned lasso model.

```{r, lasso_fit_1}
library(glmnet)
lasso_grid <- grid_regular(penalty())

lasso4_fit_1 <- tune_grid(
  mod_lasso,
  preprocessor = lasso4_rec,
  resamples = cv_splits,
  grid = lasso_grid,
  control = tune::control_resamples(verbose = TRUE,
                                    save_pred = TRUE)
)

```

### Question A
  + How many models were fit to each fold of `lasso4_fit_1`? (Please provide a numeric answer, *and* use code to corroborate your answer.)
  
```{r}
lasso4_fit_1 %>% collect_metrics()%>%
  filter(`.metric`== "rmse")
```

3 values were fitted to each fold. 

  + Use code to list the different values of `penalty()` that were used.

```{r}
lasso_grid
```

## 6. Fit another tuned lasso model

Use your code from (5) above to complete the code maze below to fit a second tuned lasso model, using the same `parsnip` model, `recipe`, and resampled object you used before.

```{r, lasso_fit_2}
lasso4_fit_2 <- tune_grid(
  mod_lasso,
  preprocessor = lasso4_rec,
  resamples = cv_splits,
  control = tune::control_resamples(verbose = TRUE,
                                    save_pred = TRUE)
)
```

### Question B

  + How many models were fit to each fold of `lasso4_fit_2`? (Please provide a numeric answer, *and* use code to corroborate your answer.)

```{r}
lasso4_fit_2 %>% collect_metrics() %>%
  filter(`.metric` == "rmse")
```
 
There were 10 models fit to each fold, since 10 is the default for tune_grid. 
 
  + If this is different than the number of models of `lasso4_fit_1`, please explain why.

In lasso4_fit_1, we used the defoult for grid_regular, which was 3. In this model, we used a different function (tune_grid), which has a different default of 10 models per fold.

  + Use code to list the different values of `penalty()` that were used for *lasso4_fit_2*.

```{r}
lasso4_fit_2 %>% collect_metrics()%>%
  select(penalty)
```

## 7. Complete the necessary steps to create and fit a tuned lasso model that has seven or more predictors (use any tuning grid you like). Note that you will need to create a new recipe as well.

```{r, lasso8}
# preprocess

lasso8_rec <- 
  recipe(
    formula = score ~ ethnic_cd + econ_dsvntg + gndr + migrant_ed_fg + lat + lon + sp_ed_fg + tag_ed_fg, 
    data = train_set #use your training set here
  ) %>%
  step_naomit(everything(), skip = TRUE) %>% 
  step_string2factor(econ_dsvntg, gndr, ethnic_cd, migrant_ed_fg, sp_ed_fg, tag_ed_fg) %>%  #may not need, depending on your formula
  step_dummy(econ_dsvntg, gndr, ethnic_cd, migrant_ed_fg, sp_ed_fg, tag_ed_fg) %>% #may not need, depending on your formula
  step_normalize(lat, lon) #may not need, depending on your formula

#fit model 

lasso_grid <- grid_regular(penalty())

lasso8_fit_1 <- tune_grid(
  mod_lasso,
  preprocessor = lasso8_rec,
  resamples = cv_splits,
  grid = lasso_grid,
  control = tune::control_resamples(verbose = TRUE,
                                    save_pred = TRUE)
)

```

## 8. Compare the metrics from the best lasso model with 4 predictors to the best lasso model with 7+ predicors. Which is best?

```{r}
# Best lasso 4 fit 1
lasso4_fit_1 %>% select_best(metric = "rmse")
best4 <- lasso4_fit_1 %>% collect_metrics() %>% filter(penalty == 0.0000000001)
best4

# Best lasso 8
lasso8_fit_1 %>% select_best(metric = "rmse")
best8 <- lasso8_fit_1 %>% collect_metrics() %>% filter(penalty == 0.0000000001)
best8
```

Lasso8 is better because the standard error is smaller compared to Lasso4 when comparing the best models of each fit. 

## 9. Fit a tuned elastic net model with the same predictors from (9). 
  + Create a new `{parsnip}` elastic net model
  + Use the same recipe from (9) above
  + Create and apply a regular grid for the elastic net model
  + Compare the metrics from the elastic net model to the best lasso model from (10). Which would you choose for your final model? What are the best hyperparameters for that model?

```{r}
(enet_params <- parameters(penalty(), mixture()))
(enet_grid <- grid_regular(enet_params, levels = c(10, 5)))
options(scipen = 999)
unique(enet_grid$penalty)
unique(enet_grid$mixture)

enet_grid <- grid_regular(enet_params, levels = c(10, 5))

#setting the model 
enet_tune_mod <- linear_reg() %>%
  set_engine("glmnet") %>% 
  set_args(penalty = tune(), 
           mixture = tune())
# Fit model 
enet_tune_mod_results <- tune_grid(
  enet_tune_mod,
  preprocessor = lasso8_rec,
  resamples = cv_splits,
  grid = enet_grid,
#  metrics = yardstick::metric_set(rmse),
  control = tune::control_resamples(verbose = TRUE,
                                    save_pred = TRUE)
)

collect_metrics(enet_tune_mod_results)

enet_tune_mod_results %>%
  show_best(metric = "rmse", n = 5)

# Best from enet
enet_tune_mod_results %>%
  select_best(metric = "rmse")

best_e <- enet_tune_mod_results %>% collect_metrics() %>% filter(penalty == 0.0000000001 & mixture == 0.75)
best_e

# Best lasso 8
best8
```

Our best elastic net model has the same standard error as our Lasso 8 model, so you could pick whichever one you want!

